Analysis

### 2023-03-28 Analysis.rmd
update tables for expert performance

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    cap = "Performance for two-week-ahead forecasts. Vallues have been cut to three significant digits and rounded.  \\label{tab:scores}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table.tex')

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    hor = 4, 
    cap = "Performance for four-week-ahead forecasts. Vallues have been cut to three significant digits and rounded \\label{tab:scores-4}"
  ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-horizon-4.tex')
```

@@

expert_ensemble$scores |>
   make_performance_table(
     scores_summarised = expert_scores_summarised,
    cap = "Performance for two-week-ahead forecasts of experts and non-experts. Standard deviations are given in brackets. \\label{tab:scores-experts}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-experts.tex')

expert_ensemble$scores |>
   make_performance_table(
     scores_summarised = expert_scores_summarised,
     hor = 4,
     cap = "Performance for four-week-ahead forecasts of experts and non-experts. Standard deviations are given in brackets. \\label{tab:scores-experts-4}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-experts-4.tex')

@@

>>>>

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    cap = "Performance for two-week-ahead forecasts. Values have been cut to three significant digits and rounded.  \\label{tab:scores}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table.tex')

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    hor = 4, 
    cap = "Performance for four-week-ahead forecasts. Values have been cut to three significant digits and rounded \\label{tab:scores-4}"
  ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-horizon-4.tex')
```

@@

expert_ensemble$scores |>
  rbind(filter(scores, model == "EuroCOVIDhub-ensemble"), fill = TRUE) |>
   make_performance_table(
     model_filter = c("Expert", "Non-Expert", "EuroCOVIDhub-ensemble"),
    cap = "Performance for two-week-ahead forecasts of experts and non-experts. Values have been cut to three significant digits and rounded. \\label{tab:scores-experts}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-experts.tex')

expert_ensemble$scores |>
  rbind(filter(scores, model == "EuroCOVIDhub-ensemble"), fill = TRUE) |>
   make_performance_table(
     model_filter = c("Expert", "Non-Expert", "EuroCOVIDhub-ensemble"),
     cap = "Performance for four-week-ahead forecasts of experts and non-experts. Values have been cut to three significant digits and rounded. \\label{tab:scores-experts-4}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-experts-4.tex')

@@

plot_ranks(expert_ensemble$scores)

# Ranks

plot_ranks <- function(scores, hor = 2) {
  scores |>
    summarise_scores() |>
    select(model, target_type, horizon, forecast_date, interval_score, scale, type_and_scale) |>
    group_by(target_type, scale, horizon, forecast_date) |>
    mutate(rank = rank(interval_score)) |>
    filter(horizon == hor) |>
    ggplot(aes(y = model, group = rank, fill = rank)) +
    geom_bar(position = position_stack(), colour = "white", size = 0.03) + 
    facet_wrap(~ type_and_scale) + 
    scale_fill_continuous(trans='reverse') + 
    theme_scoringutils() + 
    labs(y = "", x = "Frequency", fill = "Rank") + 
    theme(legend.position = "right")
}

p_ranks <- scores |>
  filter(model %in% models_non_human) |>
  mutate(model = factor(model, levels = rev(levels(models_non_human)))) |>
  plot_ranks()
ggsave("output/figures/performance-ranks.png", 
       plot = p_ranks, 
       width = 7, height = 3.4)

p_ranks_4 <- scores |>
  filter(model %in% models_non_human) |>
  mutate(model = factor(model, levels = rev(levels(models_non_human)))) |>
  plot_ranks(hor = 4)
ggsave("output/figures/performance-ranks-4.png", 
       plot = p_ranks_4, 
       width = 7, height = 3.4)
